### 2015-08-12 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
Updates in the proposal

%%%
%%% CASE FOR SUPPORT (16 pages) 
%%%
\section{Case for Support (16 pages)}
\subsection{Introduction}

@@

@@

Since the publication of the Intergovernmental Panel on Climate Change Report (IPCC, 2005) the injection of \CO in geological formations, became a viable option to mitigate GHG emissions. Depleted oil and gas reservoirs, saline aquifers and unminable coal beds are examples of potential geological formations for injection sites. Such geological repositories could provide storage for at least 2000Gt of \CO. The European Council's directive 2009/31/EC outlines key conditions that must be met to obtain a storage site permit including detailed plans to mitigate \CO leakage events and continuous monitoring of the site conditions (e.g., amount and quality of injected \CO, temperature and pressure for assessment of phase behaviour, \CO migration paths).

In Carbon Capture, Utilisation, and Storage (CCUS) integrated processes, \CO is captured from energy-intensive point sources, mitigated by either chemical conversion or injected in geological formations for either indefinite storage (CCS) or to improve hydrocarbon productivity as part of enhanced oil recovery (\CO-EOR) technologies. Each CCUS process is at very different stages of development and optimisation. Although technologies for \CO capture and chemical conversion are well-established technologies, one of the major R$\&$D focus is on retrofitting existing power plants that are in continuous development need to be optimised have benefited of years

>>>>

%%%
%%% CASE FOR SUPPORT (16 pages) 
%%%
\section{Case for Support (16 pages)}

\subsection{Background}

@@

The proposed project is focused on predicting \CO\; lateral migration and leakage in complex geological heterogeneity. For the simulation of \CO\; migration it is critically important to accurately represent geological structural characteristics (e.g., facies of the same material property, faults and fractures).  Fully unstructured tetrahedral finite elements have unrivalled geometrical flexibility and are by far the best choice to represent these complex geometries and internal boundaries. Such geological-conforming geometry representation is used with the next generation of models based upon a new family of discontinuous finite element methods. This approach promises a step-change in accuracy from conventional corner-point grids methods in industry-standard flow simulators and represents a novel contribution to CCUS technology. The new model is able to optimally adapt the mesh to represent physics of particular interest, e.g., to focus resolution in the pathways of \CO\; migration.  This model will help quantifying time-scales for supercritical \CO\; migration and potential leakage in geological repositories.

@@
